%!TEX root = ../dissertation.tex
\chapter{Project Instructions}
\label{AppendixA}

The CD is formed of three directories:
\begin{itemize}
\item src - This contains the raw code for the deliverables pulled straight
from github each project contains a README on how to build and execute it.
Both have a prerequisite on npm or yarn and an internet connection if you
wish to install them on your local pc.
\item build - This contains built versions of the deliverables which can be
hosted on a static HTTP server. It is important to note that they must be
hosted at the root directory. Opening index.html for each in a browser will
give you the full content.
 \begin{itemize}
  \item A11Y Guide - This is also available at
  \item A11Y Tool -
 \end{itemize}
\item report - This contains the report
\end{itemize}

\section{Viewing prebuilt artifacts}
\subsection{A11Y Guide}
There are few different methds for viewing the artifacts.

\subsubsection{View the version from Continuous Deployment}
It is available at: \url{https://geeman201.github.io/geemans-a11y-guide}
with the source being available at: \url{https://github.com/Geeman201/geemans-a11y-guide}

\subsubsection{Using a PHP server}
\begin{enumerate}
\item Navigate to the build/A11Y-Guide directory
\item If you have PHP install execute 'php -S localhost:8000'
\item Navigate to localhost:8080/
\end{enumerate}

\subsubsection{Using a node server}
\begin{enumerate}
\item Navigate to the build/A11Y-Guide directory
\item Install a server using 'npm install -g serve'
\item Execute 'serve -s .'
\item Navigate to localhost:5000/
\end{enumerate}

\subsection{A11Y Tool}
To demonstrate the tools capability included is html file which allows runs
the tests against itself.
\subsubsection{Through an example page}
\begin{enumerate}
\item Follow the instructions above to start HTTP server but in the
build\\A11Y-Tool directory
\item Open a browser
\item Navigate to localhost:5000/
\item If you observe a page loading with a report in the top right corner it
is successfully working.
\end{enumerate}

\subsubsection{Inject it via the devtools}
\begin{enumerate}
\item Follow the instructions above to start HTTP server but in the
build\\A11Y-Tool directory
\item Open a browser
\item Open the browsers devtools
\item Execute the command shown below to insert a script element pointing at
the deployed instance
\item Observe the tool running against your page
\end{enumerate}

\begin{lstlisting}
(function(){var head=document.getElementsByTagName('head')[0],script=document
.createElement('script');script.type='text/javascript';script
.src='http://localhost:8000/static/js/main.3d588863.js';head.appendChild
(script);})();
\end{lstlisting}


\section{Building Artifacts}
Both artifacts are built using yarn and npm and thus going into their
retrospective directories and running either `yarn build' or `npm run build'
will result in the project building a fresh version.
