%!TEX root = ../dissertation.tex
\begin{savequote}[75mm]
Nulla facilisi. In vel sem. Morbi id urna in diam dignissim feugiat. Proin molestie tortor eu velit. Aliquam erat volutpat. Nullam ultrices, diam tempus vulputate egestas, eros pede varius leo.
\qauthor{Quoteauthor Lastname}
\end{savequote}

\chapter{Evaluation}

\newthought{Realistic evaluation is a vital part of a good project report.}
For software projects, describe the evaluation methods used; discuss reliability
and usability of the end-product; where appropriate, obtain client views. To
what extent have the specified objectives of the project been met? How
successful and appropriate was the methodology adopted? Wherever possible,
support your views with evidence.
For research projects, discuss the merit of research methods/approaches
employed; if you didn’t already do so in your Deliverable chapter, compare the
merit of your methods, where applicable, with other possible alternatives,
Consider the limitations of the research, including limitations on the
generalisability of the results obtained/recommendations made/guidelines
suggested – providing sound argument for these limitations. Outline the
lessons learned as a result of the research and discuss scope and directions for
future research.
Computer Science, SEAS, Aston University – 5 – DC3010 Instructions 2016/17
This section should be answering the question: “How do I know if the
deliverable met its goals?”
Include an assessment of the business value of the deliverable.

